---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if(file.exists("shiny-events.csv")) unlink("shiny-events.csv")
```
# shinyevents

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `shinyevents` is to provide an easy way to log events ocurring within a Shiny app.  The logged events can later be analyzed to help determine things such possible improvement oportunities for an app, as well how end-users actually interact with the app itself.

## Installation

The development version pf `shinyevents` is available on [GitHub](https://github.com/):

``` r
# install.packages("remotes")
remotes::install_github("edgararuiz/shinyevents")
```


This is a basic example which shows you how to solve a common problem:

```{r example}
library(shinyevents)

tracker <- shiny_events_to_csv()
```

```{r}
tracker$app
tracker$guid
```

```{r}
tracker$entry()
```

```{r, include = FALSE}
tracker$event("example", "readme")
```


```{r}
tracker$event("example", "readme")
```

```{r}
read_events <- function()  {
  read.csv(
  "shiny-events.csv",
  stringsAsFactors = FALSE,
  col.names = c("guid", "app", "activity", "value", "datetime")
  )
}
read_events()
```

```{r}
tracker$event("start_app")
tracker$event("slider", "3")
tracker$event("stop_app")

read_events()
```

## Example

```{r, eval = FALSE}
shiny::runApp(
  system.file(
    "samples", "shinydashboard-db", 
    package = "shinyevents"
    ), 
  display.mode = "normal"
  )
```




